Computer Science House Constitution

### 2016-11-14 articles.tex
Clarified Semantic Change Discussions
Exactly when house wide discussions of semantic changes should be held is currently vague and unclear.  Currently, we have discussion on amendments one week after their proposal.  The current wording could easily be interpreted as meaning otherwise.  This change would require proposed amendments to be discussed immediately after being proposed, rather than one week later.  This change would prevent members from voting no on an amendment simply because they don't like the wording as they would have been able to discuss their issues involving wording and phr

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing for a History Disussion meeting.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
The final proposal and a summary of the discussion are presented the following week at House Meeting and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.

>>>>

\asubsection{Semantic Changes}
Any semantic change to the Constitution requires the change to be proposed in writing at a House Meeting.  
Discussion of the wording and the implications of the change should be held immediately following the proposal.
Any modifications made due to the discussion are added to the written proposal and the modified proposal is posted in the House during the week.
The final proposal is presented the following week and ballots are distributed for a ballot House vote as described in \ref{Balloted Vote}.
The ballots are collected for a minimum of a forty-eight hour period.
A quorum of two-thirds of the Total Number of Possible Votes must cast ballots for the vote to be official.
A vote equaling or exceeding two-thirds of the number of votes cast is required for the change to be placed into the constitution.
The Constitution may be overridden by an immediate House vote as described in \ref{Immediate Vote}.
There must be a quorum of eighty-five percent of the Total Number of Possible Votes for the vote to be official.
A vote equaling or exceeding ninety percent of the number of votes cast is required for the override to take effect.
